D_exp_2

### 2018-09-06 docs/D_exp_2.Rmd
github please build from /docs/

```{r, echo=FALSE, message=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
library(gridExtra)
source("D_exp_2_functions/preprocessing.R")
source("D_exp_2_functions/pretty_coef_table.R")
source("D_exp_2_functions/summarySEwithin2.R")
root_dir <- getwd()
data_dir <- "D_exp_2_data"
```

>>>>

```{r, echo=FALSE, message=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
library(grid)
library(gridExtra)
source("D_exp_2_functions/preprocessing.R")
source("D_exp_2_functions/pretty_coef_table.R")
source("D_exp_2_functions/summarySEwithin2.R")
root_dir <- getwd()
data_dir <- "D_exp_2_data"
```
